AGEAS: Automated Machine Learning based Genetic Regulatory Element Extraction System

### 2022-12-05 docs/manuscript/main.tex
v0.0.1b1

\section*{Results}
  \label{res}
  To assess predictive power of utilizing extraction result of AGEAS, we primarily applied AGEAS to study somatic reprogramming of induced pluripotent stem cells (iPSC) in mice, \cite{yamanaka_2006} a milestone discovery of cell plasticity. \cite{cell_repro_review}
  With $\sigma$ thread set to 2.0 for constraining total GRP amount in psGRNs, we use public scRNA-seq based GEMs of embryonic stem cells (ESCs) and mouse embryonic fibroblasts (MEFs) shown in Table \ref{geo_table} as inputs.
  The extraction result can be summarized as TF regulons, and TFs with highest regulatory degree in extracted GRN atlas are marked as top TFs (Figure \ref{result_figs}a).

@@

        Here we address AGEAS's applicability on cell pathological development studies through analyzing hepatic stellate cells (HSCs) and portal fibroblasts (PFs) simulating activated HSCs in mice liver administrated with chronic carbon tetrachloride ($CCl_4$) for six weeks.

>>>>

\section*{Results}
  \label{res}
  To assess predictive power of utilizing extraction result of AGEAS, we primarily applied AGEAS to study somatic cell reprogramming to induced pluripotent stem cells (iPSCs) in mice, \cite{yamanaka_2006} a milestone discovery of cell plasticity. \cite{cell_repro_review}
  With $\sigma$ thread set to 2.0 for constraining total GRP amount in psGRNs, we use public scRNA-seq based GEMs of embryonic stem cells (ESCs) and mouse embryonic fibroblasts (MEFs) shown in Table \ref{geo_table} as inputs.
  The extraction result can be summarized as TF regulons, and TFs with highest regulatory degree in extracted GRN atlas are marked as top TFs (Figure \ref{result_figs}a).

@@

        Here we address AGEAS's applicability on cell pathological development studies through analyzing hepatic stellate cells (HSCs) and portal fibroblasts (PFs) simulating activated HSCs in mice liver administrated with carbon tetrachloride ($CCl_4$) for six weeks.
